AggregateCounts

### 2021-06-07 R/AggregateCounts.Rmd
import and fancy histogram working for 1 sample

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
filter <- dplyr::filter

ReadAggregateFile(fileList[1], "Pa", "1", "wt")
blah<-GetAggregates()

datos <-read.csv(fileList[1], header = F)
colnames(datos)<-c('Size')
datos1<-datos %>% filter(!Size<0.5) #first filter the size

ReadAggregateFile<-function(file, species, timepoint, condition, replicate){#make a dataframe of the aggregate size list and add experimental parameters
   datos <-read.csv(file, header = F)
   colnames(datos)<-c('Size')
   datos<-datos %>% filter(!Size<0.5) #first filter the size
   datos<-datos %>% mutate(Species = species)#add parameters
   datos<-datos %>% mutate(TimePoint = timepoint)
   datos<-datos %>% mutate(Condition = condition)
   datos<-datos %>% mutate(Replicate = replicate)
   datos$Species<-as.factor(datos$Species)
   datos$Replicate<-as.factor(datos$Replicate)
   datos$Condition<-as.factor(datos$Condition)
   datos$TimePoint<-as.factor(datos$TimePoint)
   return(datos)
}

GetAggregates<-function(){#import all experiments at once
   folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
     }
   return(growthDf)
}
```

>>>>

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
library(plotrix)#for std error
library(cowplot)
filter <- dplyr::filter

aggregateList<-GetAggregates()
# mutate(Strain = recode(Position, "0" = "Pa14 wt", "1"= "Pa14 -PA1414","2" = "Pa14 wt", "3"= "Pa14 -PA1414")) #this is to change the names

#agregate input functions
#####
ReadAggregateFile<-function(file, species, timepoint, condition, replicate){#make a dataframe of the aggregate size list and add experimental parameters
   datos <-read.csv(file, header = F)
   colnames(datos)<-c('Size')
   datos<-datos %>% filter(!Size<0.5) #first filter the size
   datos<-datos %>% mutate(Species = species)#add parameters
   datos<-datos %>% mutate(TimePoint = timepoint)
   datos<-datos %>% mutate(Condition = condition)
   datos<-datos %>% mutate(Replicate = replicate)
   datos$Species<-as.factor(datos$Species)
   datos$Replicate<-as.factor(datos$Replicate)
   datos$Condition<-as.factor(datos$Condition)
   datos$TimePoint<-as.factor(datos$TimePoint)
   return(datos)
}

GetAggregates<-function(){#import all experiments at once
   folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
     }
   return(growthDf)
}
#####
```
```{r aggregate wrangling}
aggregateListSummary<-aggregateList %>% group_by(Species, TimePoint, Condition) %>% 
  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass )

#plot agg summary
#####
ggplot()+
  geom_point(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"))+
  geom_point(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"))+
  geom_point(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"))+  
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(. ~ Condition, scales = "free", space = "free") +
  ggtitle('Aggregates: Mean, largest and total biomass (wild type)')+
  labs(x = "",y = "Aggregate size (um3)")+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#####

#create histograms, this takes a long time, so consider cutting them in chunks
allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition)#first do the correct grouping
allDataList<- group_split(allDataGrouped)#create list of dataframes
allDataHistograms.5<-map2(allDataList, 5,TotalFancyHistogram)#apply histogram function to all items in the list

allDataHistograms.5df<- bind_rows(allDataHistograms.5)

```
```{r Histogram fucntions}
FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin
  results<-data.frame()
  for( i in 1:(length(sec)-1)){ 
    blah<-df %>% filter(Size > sec[i] &Size<=sec[i+1])%>%summarise(frequency = n(), avg = mean(Size),suma = sum(Size)) %>% mutate(bin = i, min = sec[i],max = sec[i+1])
    if(blah$frequency>0){ 
      results<-rbind(results, blah)} 
  }
  return(results) 
}
TotalFancyHistogram<-function(df,binsize){
  totalbiomass<-sum(df$Size)#total biomass per sample
  totalfrequency<-length(df$Size)#total number of objects
  upperLim<-max(df$Size)+binsize-(max(df$Size)%%binsize)#largest bin size based in largest object
  breaksSequence<-seq(0,upperLim,binsize)#this makes breaks every "binsize" 
  histogram<-FancyHistogram(df,breaksSequence)#apply "fancy histogram" to get distributions
  histogram%>%mutate(BiomassBin=suma/totalbiomass)->histogram#add column with proportion of biomas per bin
  histogram%>%mutate(Density=frequency/totalfrequency)->histogram#add column with proportion of counts per bin
  histogram%>%mutate(Species=df$Species[1])->histogram#add column maintaining sample and so on...
  histogram%>%mutate(Condition=df$Condition[1])->histogram
  histogram%>%mutate(TimePoint=df$TimePoint[1])->histogram
  histogram%>%mutate(Sample=df$Sample[1])->histogram
  return(histogram)
}
```
